Revealing the rich and varied dynamics of hippocampal replay

### 2020-09-02 Article.tex
Update on Overleaf.

\begin{figure}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure3-supplemental2/Figure3_v1-supplemental2}
\caption{Comparison of real vs. position shuffled data for two epochs from different animals. Line represents the percent of SWR events classified in that epoch for real data. The histogram represents the distribution after 50 shuffles of the position data. Position data was shuffled by resampling with replacement from the set of all observed positions in that epoch, destroying position information but preserving spiking timing and position occupancy.}
\label{fig:Figure3-Figure supplement 2}
\end{figure}

>>>>

\begin{figure}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure3-supplemental2/Figure3_v2-supplemental2}
\caption{Comparison of speed classification on real vs. position shuffled data for two epochs from different animals. Line represents the percent of SWR events classified in that epoch for real data. The histogram represents the distribution after 50 shuffles of the position data. Position data was shuffled by resampling with replacement from the set of all observed positions in that epoch, destroying position information but preserving spiking timing and position occupancy.}
\label{fig:Figure3-Figure supplement 2}
\end{figure}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure4-supplemental1/Figure4_v1-supplemental1}
\caption{Comparison of average spatial coverage of the 95\% highest posterior density on real vs. position shuffled data for two epochs from different animals. Line represents the average spatial position spanned by the highest posterior density on real data for all ripples. The histogram represents the distribution after 50 shuffles of the position data. Position data was shuffled by resampling with replacement from the set of all observed positions in that epoch, destroying position information but preserving spiking timing and position occupancy.}
\label{fig:Figure4-Figure supplement 1}
\end{figure*}
